---
title: "US Fish & Wildlife Service Color Palettes"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE,
                      message = FALSE)
```

## Description

Inspired by [this tweet](https://twitter.com/margaretsiple/status/1306695097438801920) from Dr. Margaret Siple this is a minimal package designed to add color palettes based on the photos. This package was developed at the same time DL Miller created [a gist](https://gist.github.com/dill/1729bbc9ad4f915942045f96a6cfbf9d) to allow people to use those palettes as well. 
This package aims to allow users to install the functions needed to use these palettes.

## How to Get

You can get this package using the remotes pacakge by typing

`remotes::install_github("delabj/USFWSpalettes")`

or with devtools 

`remotes::install_github("delabj/USFWSpalettes")`

## What's Inside

This package contains a few basic functions and lists.

+ `USFWS_palettes`(List of Palettes)
+ `USFWS_palette()`
+ `scale_color_USFWS()`
+ `scale_fill_USFWS()`

## Useage


```{r}
library(tidyverse)
library(USFWSpalettes)

# Get a palette
USFWS_palette(5, "aurora", TRUE)


diamonds %>%
  ggplot(aes(x=cut, fill=cut))+
  geom_bar()+
  theme_minimal()+
  scale_fill_USFWS()+
  labs(title = "Count of Diamonds by Cut")

```





## Palettes Included

The following is an example of all palettes included.

```{r, echo=FALSE}

par(mfrow=c(2,3))
USFWS_palette(5, "dolly", TRUE)
USFWS_palette(5, "sockeye", TRUE)
USFWS_palette(5, "coaster", TRUE)
USFWS_palette(5, "aurora", TRUE)
USFWS_palette(5, "florida", TRUE)

```

